A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-15 paper/paper.tex
Notation fight

Let $G$ and $H$ be the two input graphs to our maximum common subgraph problem.
The orders (vertex counts) of these graphs are denoted $n_G$ and $n_H$. We will
use $n$ in complexity results to denote $\max(n_G + n_H)$.

@@

\paragraph{Efficient representation of label classes} The algorithm as
described so far requires $\BigO{n^2}$ space at each level of the search tree,
since labels may be up to $n_G$ bits in length. We can reduce the memory
requirement to $\BigO{n}$ per level by storing a \emph{label class} as a pair
$\langle P,T \rangle$ for each label $l$ that is used, where $P$ is the set of
vertices in $\V(G)$ labelled $l$, and $T$ is the set of vertices in $\V(H)$
labelled $l$.\footnote{We adopt terminology from subgraph isomorphism where one
graph is a pattern graph $P$ and the other the target graph $T$.} Since there
are $n_G + n_H$ vertices in the two graphs, at most $n_G + n_H$ label classes
can exist at once, and there are at most $n_G + n_H$ vertices in the union of
all of the $P$ and $T$ sets.  We can gain further efficiency by discarding
during search any label class that has an empty $P$ or $T$ set.

@@

\McSplit\ requires $\BigO{n}$ time at each search node, and does not require
any auxiliary data structures larger than the adjacency matrices of $G$ and $H$
to be built prior to search.  CP-FC requires $\BigO(?????)$ \dots The clique
encoding requires an association graph with $n_G n_H$ vertices to be
constructed before search.  Modern maximum-clique algorithms typically perform
a colouring step at each search node that is quadratic in the order of the
graph, and thus $\BigO{n^4}$ in the order of the max common subgraph input
graphs.

@@

\paragraph{Undirected with edge labels} Each adjacency matrix
entry contains an edge label, or a null entry (non-adjacent) $0$.
We use Algorithm~\ref{labDirAlg}, by letting $L$ be
the union of $\{0\}$ with the set of all labels that appear in the input
graphs. Since there may be up to $n_G + n_H$ distinct labels, the loop in
Algorithm~\ref{labDirAlg} may execute up to $n_G + n_H$ times and
requires $\BigO{n^2}$ time per search
node.  It is possible to modify the algorithms to run in $\BigO{n \log n}$ per
search node.  First, run lines 17-19
of Algorithm~\ref{McCliqueAlg} to create a new label-class of vertices that are not
adjacent to $v$ or $w$, and remove these vertices from $\langle P',T' \rangle$.
Next, sort $P'$ and $T'$ in ascending order of the label on the edge from $v$
or $w$ to each vertex. We can then create the label classes corresponding to
each edge label by simultaneously traversing $P'$ and $T'$ from left to right.

@@

\paragraph{Top-Down Strategy} I'VE RE-ADDED A SHORTER VERSION OF THIS
PARAGRAPH, WHICH WAS COMMENTED OUT BY PATRICK. IT NEEDS WORK, BUT WE NEED TO
EXPLAIN THE SIP EXPERIMENT. We can modify the \McSplit\ algorithm to use a
top-down strategy based on \citet{UpcomingAAAIPaper} by calling the main
\FuncSty{McSplit} method once per goal size ($n_G, n_G-1, n_G-2, \dots$).  We
backtrack (\lineref{PruneSearch} of Algorithm~\ref{McCliqueAlg}) when the bound is
strictly less than the goal size, and terminate when a solution of the goal
size is found.

>>>>

Let $G$ and $H$ be the two input graphs to our maximum common subgraph problem.
The orders (vertex counts) of these graphs are denoted $g$ and $h$. We will
use $n$ in complexity results to denote $\max(g + h)$ ?? WTF James? Help?.

@@

\paragraph{Efficient representation of label classes} The algorithm as
described so far requires $\BigO{n^2}$ space at each level of the search tree,
since labels may be up to $g$ bits in length. We can reduce the memory
requirement to $\BigO{n}$ per level by storing a \emph{label class} as a pair
$\langle P,T \rangle$ for each label $l$ that is used, where $P$ is the set of
vertices in $\V(G)$ labelled $l$, and $T$ is the set of vertices in $\V(H)$
labelled $l$.\footnote{We adopt terminology from subgraph isomorphism where one
graph is a pattern graph $P$ and the other the target graph $T$.} Since there
are $g + h$ vertices in the two graphs, at most $g + h$ label classes
can exist at once, and there are at most $g + h$ vertices in the union of
all of the $P$ and $T$ sets.  We can gain further efficiency by discarding
during search any label class that has an empty $P$ or $T$ set.

@@

\McSplit\ requires $\BigO{n}$ time at each search node, and does not require
any auxiliary data structures larger than the adjacency matrices of $G$ and $H$
to be built prior to search.  CP-FC requires $\BigO(?????)$ \dots The clique
encoding requires an association graph with $g h$ vertices to be
constructed before search.  Modern maximum-clique algorithms typically perform
a colouring step at each search node that is quadratic in the order of the
graph, and thus $\BigO{n^4}$ in the order of the max common subgraph input
graphs.

@@

\paragraph{Undirected with edge labels} Each adjacency matrix
entry contains an edge label, or a null entry (non-adjacent) $0$.
We use Algorithm~\ref{labDirAlg}, by letting $L$ be
the union of $\{0\}$ with the set of all labels that appear in the input
graphs. Since there may be up to $g + h$ distinct labels, the loop in
Algorithm~\ref{labDirAlg} may execute up to $g + h$ times and
requires $\BigO{n^2}$ time per search
node.  It is possible to modify the algorithms to run in $\BigO{n \log n}$ per
search node.  First, run lines 17-19
of Algorithm~\ref{McCliqueAlg} to create a new label-class of vertices that are not
adjacent to $v$ or $w$, and remove these vertices from $\langle P',T' \rangle$.
Next, sort $P'$ and $T'$ in ascending order of the label on the edge from $v$
or $w$ to each vertex. We can then create the label classes corresponding to
each edge label by simultaneously traversing $P'$ and $T'$ from left to right.

@@

\paragraph{Top-Down Strategy} I'VE RE-ADDED A SHORTER VERSION OF THIS
PARAGRAPH, WHICH WAS COMMENTED OUT BY PATRICK. IT NEEDS WORK, BUT WE NEED TO
EXPLAIN THE SIP EXPERIMENT. We can modify the \McSplit\ algorithm to use a
top-down strategy based on \citet{UpcomingAAAIPaper} by calling the main
\FuncSty{McSplit} method once per goal size ($g, g-1, g-2, \dots$).  We
backtrack (\lineref{PruneSearch} of Algorithm~\ref{McCliqueAlg}) when the bound is
strictly less than the goal size, and terminate when a solution of the goal
size is found.
